\documentclass[10pt]{article}
\usepackage[a4paper, left=0.40in, right=0.40in, top=0.25in, bottom=0.2in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{fontawesome}
\hyphenation{Some-long-word}

\usepackage{resume}

\begin{document}
	
\begin{center}
	\textbf{\LARGE Siddarth Meenakshisundaram}\\[0.5ex]
	\textscale{1.05}{7655 Palmilla Dr,Apt. 4102, San Diego, CA 92122\\
		\faEnvelopeO \hspace{0.1ex} \href{mailto:simeenak@ucsd.edu}{simeenak@ucsd.edu}
		\hspace{5ex}
		\faLinkedin  \href{https://linkedin.com/in/siddarthm}{\linkedin{\hspace{0.1cm}linkedin.com/in/siddarthm}}
		\hspace{5ex}
		\faGithub \href{https://github.com/Siddarth-M}{\hspace{0.1cm}github.com/Siddarth-M}
		\hfill
		\faPhone \hspace{0.1ex} +1 (858) 337-4537}	
\end{center}
\spacedhrule{-1.0ex}{-0.5ex}

\roottitle{EDUCATION}

\headedsection
{University of California, San Diego | Jacobs School of Engineering}
{San Diego, CA}
{Master of Science in Mechanical and Aerospace Engineering}
{{Expected Graduation: }{June 2021}{}{}}
{Ongoing Courses: Mathematics for Engineers, Machine Learning for Image Processing, Linear Systems Theory}

\headedsection
{National Institute of Technology, Tiruchirapalli   }
{Trichy, India}
{Bachelors of Technology in Instrumentation and Control Engineering}
{\period{Aug}{2015}{May}{2019}}
{Relevant Courses: Classical and Modern Control Systems, Engineering Mechanics, Numerical Methods, Algebra and Probability Theory, Neural Networks and Fuzzy Logic}%\\
%All India rank 610 among half a million students appearing for entrance examination to IITs}


\spacedhrule{0.8ex}{0.0ex}

\roottitle{EXPERIENCE}

\headedsection
{\href{https://www.nitt.edu/}{National Institute of Technology}}
{Trichy, India}
{Cuff-less Blood Pressure Prediction using ML, CNN and LSTM}
{\period{Nov}{2018}{May}{2019}}{
\vspace{-2.4ex}
\begin{circlist}	
	%\item Operated as a team for prediction of Blood pressure from ECG and PPG signals using various ML and DL models.
	\item Proposed a new architecture using a combination of Convolutional neural networks (CNN) and Long short-term memory (LSTM) to predict Systolic Blood Pressure (SBP) and Diastolic Blood Pressure (DBP) using Python/Tensorflow.
	\item Implemented network achieves a MAE of 8.823 mmHg and 6.763 mmHg for SBP and DBP respectively.
	\item Outperformed all the existing models in the literature along with an added advantage of faster prediction and no manual feature extraction.
\end{circlist}
}

\headedsection
{\href{https://www.linedata.com/}{Indian Institute of Technology}}
{Chennai, India}
{Design, Fabrication, Control and Testing of Stewart Platform}
{\period {May}{2018}{Jun}{2018}}
{\vspace{-2.4ex}
	\begin{circlist}
		\item Calibrated an IMU (MPU-9025) and integrated with MG996R Servo and Arduino to control the Stewart platform 
		\item Utilized Complimentary filter for combining accelerometer and gyroscope mesurements(sensor fusion) in real time. 
		\item Simulated the roll, pitch and yaw of a system. The final Stewart platform fabricated has high accuracy($>$99.9\%) and \newline precision in all 6 axes.
	\end{circlist}
}

\headedsection
{\href{https://www.iist.ac.in/}{Indian Institute of Space Science and Technology}}
{Trivandrum, India}
{Control of Simulated Serial Chain Manipulator}
{\period{May}{2017}{Jun}{2017}}
{\vspace{-2.4ex}
	\begin{circlist}
		\item  Controlling a serial manipulator with six or more joints with simulation done using MATLAB and Adams. 
		\item Learned usage of Linux, Robotic Operating System (ROS) and Gazebo during this process for simulation in various environments. 
		\item Integrated Adams with MATLAB for the final simulation to control the chain manipulator.
	\end{circlist}
}

\spacedhrule{0.8ex}{0.0ex}
\roottitle{COURSEWORK PROJECTS}

\headedsectiontwo
{Multi-Object detection using Deep Learning}{\period{Oct}{2019}{Ongoing}}
{\href{https://www.charles-deledalle.fr/pages/}{Dr. Charles Deledalle}}
{\vspace{-2.4ex}
    \begin{circlist}
        \item Achieve multi-object detection with various deep learning models such as R-CNN, Fast R-CNN, Faster R-CNN, R-FCN, You look only once, Single Shot Detector etc. using Python with Tensorflow, Pytorch packages.
        %\item Backtested portfolios had higher Sharpe, lower skew, kurtosis, drawdown compared to benchmark and baseline models.
    \end{circlist}
}

\headedsectiontwo
{Prepaid Energy Supply system}{\period{Jul}{2018}{Nov}{2018}}
{\href{https://www.nitt.edu/home/academics/departments/ice/faculty/bennet/}{Dr. Goldin R Bennet}}
{\vspace{-2.4ex}
    \begin{circlist}
        \item Created a marketable prepaid system that comprised of Arduino(C programming), GSM Module, Node MCU and Relay, which is 50\% cheaper than existing models.
	    %\item Backtested portfolios ($>$1.2 IR) based on single \& combined signals of Value, Momentum, Carry, and Defensive
    \end{circlist}
}

%\headedsectiontwo
%{Systematic Underpricing in Convertible Bonds}{\period{Jul}{2018}{Oct}{2018}}

%{\vspace{-2.4ex}
 %   \begin{circlist}
  %      \item Built trading strategy based on convertible bond mispricing by implementing trinomial tree pricing models in Python
   % \end{circlist}
%}

\spacedhrule{0.8ex}{0.0ex}
\roottitle{ACHIEVEMENTS}

\headedsectionthree
{ACADEMIC} {{}{}{}{}}
{}
{\vspace{-4.5ex}
    \begin{circlist}
        \item \textbf{Gold Medallist}, All India Rank 1 in the Instrumentation Stream of Indian Engineering Olympiad 2018 conducted by Gateforum India.
        %\item Cleared first stage, Indian National Astronomy Olympiad (INAO) and was among the top 2\% students of 11000 participants.
        \item \textbf{NTSE Scholar}, was among the top 0.01\% of 1.3 million candidates who took up the examination.
        \item \textbf{Young Achiever Award}, Awarded by my school for exceptional performance in academics and sports.
    \end{circlist}
}

\headedsectionthree
{CHESS} {{}{}{}}
{}
{\vspace{-4.5ex}
    \begin{circlist}
	    \item \textbf{Captain} of College Chess Team.
	    \item \textbf{International player} with a FIDE rating of 2149. Ranked among top 0.1\% chess players in the world.
	    \item  Represented India in \textbf{Commonweath Chess Championship} in 2010 and other international events.
    \end{circlist}
}

\spacedhrule{0.8ex}{0.0ex}

\roottitle{SKILLS}

\begin{indentsection}
    \skill{Coding}{Python, C/C++}
    \skill{Simulation/Design}{Matlab, ROS, Adams, TINA, PSpice, Gazebo}
    \skill{Software/Packages}{MS Office, \LaTeX, Pytorch, Tensorflow, Keras, CUDA}
	\skill{Languages}{English, Tamil, Hindi, German(A1)}
	\skill{Certifications}{Aerial Robotics, Computational Motion Planning, Mobility in Robotics - Coursera}
%	\skill{Interests}{Strategy Games, Music, Adventure Sports}
\end{indentsection}

\end{document}
